\chapter{Deployment Technologies}
	\section{Visual Studio}
		\vspace{5mm}
	    \begin{multicols}{2}
		\paragraph{}
		
		Visual Studio an integrated development environment (IDE) is the axe of an serious wielding developer.
		This fully features integrated development environment (IDE) supports a multitude of different project types,
		catering for all possible scenarios for the current age.  The editor itself supports all the features you would expect in an 
		integrated development environment (IDE), such as code refactoring tools, autocompletion (intelliSense), 
		class designers, code versioning and database schema designers, but takes it to a whole new level by the sheer attention to detail and implementation of these features make the environment a joy to work in and extremely productive.    
			
		\end{multicols}
		
	\section{C\#}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		CSharp is a multi-paradigm language, to name a few imperative, declarative, functional and object oriented.  
		The language developed by Microsoft is sworn by some to be the successor to Java.  This strongly types language
		reintroduced many of the favored keywords such as virtual and such notable additions such as override which negate
		the need for interpretation and annotations seen in the java environment.  C\# itself is compiled into a command language runtime format
		like Java and as such can to be ran an any architecture that implements the .NET runtime.  Such notable ports include Mono originally 
		developed by Novel before going open source.   

		\end{multicols}

	\section{Windows Communication Foundation}
		\subsection{Introduction}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		Windows Communication Foundation (WCF) is a part of the .NET Framework that provides a unified programming model for 
		rapidly building service-oriented applications (SOA) that communicate across the web.  The implementation of these applications is typically 
		hosted on Internet Information Servers (IIS) which exposes the application to web requests.  Windows Communication Foundation (WCF) 
		realizes service oriented architectures principles to support clients in the distributed computing environment.  The server 
		implementation publishes it service for a Web Service Description Language (WSDL) typically in the Extendable Markup Language (XML) 
		to which clients can subscribe to in order to consume or produce ( send \& receive ) information to and from the service.

		\end{multicols}
		
		\subsection{Service Contracts}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		In Windows Communication Foundation (WCF), service contracts are interfaces to which clients program to and service implementers realize.
		These interfaces are exactly the same as a normal interface in an object oriented language except special annotations [ServiceContract] \&
		[OperationContract] are used to defined what will be exposed as part of the Web Service Description Language(WSDL) to which clients will
		subscribe to.
		
		\end{multicols}
		
		\subsection{Data Contracts}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		In Windows Communication Foundation (WCF), data contracts are formal agreements between clients and the service regards data type, it's 
		mechanism for defining	abstract data types as the exchange information.
		A data contract is implemented as normal class to which special annotations are added, namely [DataContract] \& [DataMember].  These annotations
		respectively define whether a class and its members should be exposed as part of the Web Service Description Language(WSDL) service contract. 

		\end{multicols}
		
	\section{Windows Presentation Foundation}
		\subsection{Model View Controller}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		Windows Presentation Foundation Applications (WPF) is a model view controller User Interface Designer for rendering user interfaces.
		The separation of concerns primarily, business logic( controller ) and the interface design( view ).  The controller can be written
		in any of the .Net family languages and the view is written in Xaml ( XML ).  This allows clear separation of the interface from the business logic
		and allows different controllers written in different .NET languages to use the same interface consistently.
		Windows presentation foundation itself is a graphical subsystem built on top of DirectX allowing for greater efficiency over the old Graphical 
		Device Interface ( GDI ) system. 

		\end{multicols}
		
		\subsection{View}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		The view in Windows Presentation Foundation Applications (WPF) is written in Extensible Application Markup Language (XAML) is a declarative language 
		used in the specification of user interfaces comprised of controls such as buttons, text boxes, windows etc.  The specification supports data binding, 
		eventing and other features as a means to simplify the designing user interfaces. 
		business logic

		\end{multicols}
		
		\subsection{Controller}
		\vspace{5mm}
		\begin{multicols}{2}
		\paragraph{}
		
		The controller in Windows Presentation Foundation Applications (WPF) can be written in any of the .NET family languages, its bound to the view at runtime 
		and implements event handlers that accept the events that are generated for the view.  

		\end{multicols}