\chapter{Project Charter}
\setcounter{page}{1}
	\section{Introduction}
		\paragraph{}
			\vspace{10mm}
				A project charter is a document that formally recognizes the existence of a project and 
				provides direction on the project’s objectives and management.  It authorizes the project 
				manager to use  organizational resources to complete the project.  Key project stakeholder’s 
				should sign a project charter to acknowledge agreement on the need for and the intent of the 
				project.
			\newline
				
	\section{Charter}
		\paragraph{}
			\vspace{10mm}
			\textbf{Project Title:} Opening a new MegaGlobalCorpSuperInc branch in Ireland.
			\newline\newline
			\textbf{Date of Authorization:} October 1
			\newline\newline
			\textbf{Project Start Date:} October 1
			\newline\newline
			\textbf{Project Finish Date:} October 1 2013
			\newline\newline
		
		\paragraph{}
			\vspace{5mm}
			\textbf{Key Milestones:} 
			\begin{itemize}
			\item Office fully operational with 50 developers by April 1 2012
			\item First version of software released by October 1 2012
			\item Scale up operations to 200 developers after October 1 2013
			\end{itemize}
				
		\paragraph{}
			\vspace{10mm}
			\textbf{Budget Information:} \newline The company has allocated €5 million for this project based on early budget estimates and more funds are available if necessary.
			\newline\newline
			
		\paragraph{}
			\vspace{5mm}
			\textbf{Project Manager:}  Yerenca Fernandez
			\newline\newline

		\paragraph{}
			\vspace{5mm}
			\textbf{Project Objectives:} \newline Our new Irish branch will be a software development house for MegaGlobalCorpSuperInc internal IT needs. 
			It is a crucial project for our company to continue to grow in a competitive market. 
			This is the first charter for the project and the objectives are to have the branch fully 
			operational with 50 developers in 6 months, to release the first version of software to our 
			internal customer by the end of year 1 and to scale up to 200 developers by the end of year 2.
			\newline\newline

		\paragraph{}
			\vspace{5mm}
			\textbf{Main Project Success Criteria:} 
			\newline
			The branch must be fully operational with 200 developers by October 1 2013. The software must meet all 
			specified criteria, be thoroughly tested and have its first major release within 12 months.
			\newline\newline

		\paragraph{}
			\vspace{5mm}
			\textbf{Approach:} 
			\newline
			\begin{itemize}
			\item Hold weekly progress review meetings with all the core project team.
			\item Within one month develop a clear work breakdown structure, scope verification plan and project schedule.
			\item Picking and setting up of Office, server and network hardware within 2 months.
			\item Purchase all required hardware within 3 months
			\item New Employee Orientation to be completed for initial employees and 50 developers by month 6
			\item Conduct thorough software testing per approved test plans
			\end{itemize}
			
			\paragraph{}
				\vspace{10mm}
				\textbf{Roles and Responsibilities:} 
				\newline

				\begin{tabular}{ | >{\scriptsize}p{35mm} | >{\scriptsize}p{25mm} | >{\scriptsize}p{25mm} | >{\scriptsize}p{40mm} | }
					\hline

					\textbf{Name} 			& \textbf{Role} 	& \textbf{Position} 	& \textbf{Contract Information}  	\\ \hline
					Vispi Shroff	 		& Sponsor 			& CEO 					& Vispi.Shroff@lero.ie 				\\ \hline
					\rowcolor[gray]{.98}
					Yerenca Fernandez	 	& Team Member 		& Project Manager	 	& dmz.oneill@gmail.com 				\\ \hline
					Alan Casey		 		& Team Member 		& Team Member			& alancasey20@gmail.com 			\\ \hline
					\rowcolor[gray]{.98}
					David O'Neill	 		& Team Member 		& Team Member		 	& yerenka@gmail.com 				\\ \hline
					Jun He	 				& Team Member 		& Team Member		 	& ilovefjjq@gmail.com 				\\ \hline
					\rowcolor[gray]{.98}
					Eoin Murphy	 			& Team Member 		& Team Member 			&  							\\ \hline

				\end{tabular}